---
title: "LogLink Logistic regression AQI data"
author: "Michael Andreae"
output: pdf_document
---

# Insurance status predicts antiemetic use 
we build a random effects model with procedure as random effects

```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr) # required to set options in Markdown R
library(lme4)
# library(nlme)
```



```{r, global_options, echo=FALSE}
# set options
opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
rm(list = ls())
everything<-FALSE
```

# Load cleaned complete case dataset
 
we load the cleaned dataset with procedure information *myAQI.Rdata* which we generated in the Project *AQI_Import*.   


```{r, load_clean_dataset, echo=TRUE}
load("Data/myAQI.Rdata")
str(myAQI)
```

# Logit Models

# Four Predictors

## Fixed Effects Model 

Link : logit
fitted with glm with **four** predictors: 

formula0 <- ond ~ pay +age_group +sex

```{r, log0, echo=TRUE, eval=everything}

formula0 <- ond ~ pay +age_group +sex

fit_log0 <- glm(formula0, 
             family = binomial(link = "logit"), 
             data = myAQI)
```

## Random Effects Model

fitted with glmer and procedure as random effect

```{r eval=everything, echo=TRUE}
formulaR0 <- ond ~ pay +age_group +sex + (1 | cpt)

m <- glmer(formulaR0, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"),
           nAGQ = 10)
save(fit_log0, m, file = "Results/zero.Rdata")
```


## Comparison of random versus Fixed effects model

```{r}
load("Results/zero.Rdata")
```

### Details Fixed Effects

```{r}
summary(fit_log0)
p_values <- summary.glm((fit_log0))$coefficient[,4]
ORfixed <- exp(coef(fit_log0)) # exponentiated coefficients 
# CI_fitlog<- confint(fit_log) # 95% CI for the coefficients, takes too long
kable(data.frame(ORfixed, p_values), digits = 3, caption = "Results log0")
```

### Details Random Effects

```{r}
summary(m)
ORrandom <- exp(m@beta) # exponentiated coefficients
```


### Random v. Fixed Side by Side 

```{r}
compareCoef <- data.frame(random=m@beta, fixed=coef(fit_log0))
kable(compareCoef, caption = ("Coefficients"))

compareOR <- data.frame(random=ORrandom, fixed= ORfixed)
kable(compareOR, caption = ("Odds ratios"))
```

# Five predictors

## Second Random Effects Model

fitted with glmer and procedure as random effect
adding ASA status

```{r eval=everything, echo=TRUE}
formulaR2 <- ond ~ pay +age_group +sex + ASA + (1 | cpt)

m2 <- glmer(formulaR2, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"),
           nAGQ = 10)

save(m2, file = "Results/second.Rdata")
```


### Details Second Random Effects Model

```{r}
load("Results/second.Rdata")
summary(m2)
ORrandom2 <- exp(m2@beta) # exponentiated coefficients
compareOR2 <- data.frame(random2= ORrandom2[1:10], random0 = ORrandom, fixed = ORfixed)
kable(compareOR2, caption = ("Odds ratios random effects model 2"))
```


# Six  predictors, two random effects

## Third Random Effects Model 

fitted with glmer and procedure as random effect
adding  a seond random effect (practice)


```{r eval=everything, echo=TRUE}
formulaR3 <- ond ~ pay +age_group +sex + ASA + (1 | cpt) +(1 | practice)

m3 <- glmer(formulaR3, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"))

save(m3, file = "Results/third.Rdata")
```

```{r}
load("Results/third.Rdata")
```

### Details Third Random Effects Model

```{r}
summary(m3)
ORrandom3 <- exp(m3@beta) # exponentiated coefficients
compareOR3 <- data.frame(random3= ORrandom3[1:10], random2= ORrandom2[1:10], random0 = ORrandom, fixed = ORfixed)
kable(compareOR3, caption = ("Odds ratios random effects model 3"))
```


# Seven  predictors, two random effects

## Fourth Random Effects Model 

fitted with glmer and procedure as random effect
adding  a seond random effect (practice) and more predictors (anes_type and ASA)


```{r eval=everything, echo=TRUE}
formulaR4 <- ond ~ pay +age_group +sex + ASA + anes_type+ (1 | cpt) +(1 | practice)

m4 <- glmer(formulaR4, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"))

save(m4, file = "Results/forth.Rdata")
```

### Details Forth Random Effects Model

```{r}
load("Results/forth.Rdata")
summary(m4)
ORrandom4 <- exp(m4@beta) # exponentiated coefficients
compareOR4 <- data.frame(random4 = ORrandom4[1:10], random3 = ORrandom3[1:10], random2= ORrandom2[1:10], random0 = ORrandom, fixed = ORfixed)
kable(compareOR4, caption = ("Odds ratios random effects model 3"))
```

# Log Link

## Log Link Random Effects Model

fitted with glmer and procedure as random effect

```{r eval=FALSE, echo=TRUE, warning=FALSE}
formulaR0 <- ond ~ pay +age_group +sex + (1 | cpt)

ml0 <- glmer(formulaR0, data = myAQI, family = binomial(link = "log"), 
           control = glmerControl(optimizer = "bobyqa"),
           nAGQ = 10)
save(ml0, file = "Results/zeroLog.Rdata")
```

The model does not seem to run:
*Error: (maxstephalfit) PIRLS step-halvings failed to reduce deviance in pwrssUpdate*

# Convergence 

## Optimized Fourth Random Effects Model 

fitted with glmer and procedure as random effect with **optimizer** *nloptwrap*
adding  a second random effect (practice) and more predictors (anes_type and ASA)

### Random Model 4 with optimizer nloptwrap

```{r eval=everything, echo=TRUE}
formulaR4 <- ond ~ pay +age_group +sex + ASA + anes_type+ (1 | cpt) +(1 | practice)

opt4 <- glmer(formulaR4, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "nloptwrap"))

save(opt4, file = "Results/optim4.Rdata")
```

### Results

```{r}
load("Results/optim4.Rdata")

ORrandomOPT4 <- exp(opt4@beta) # exponentiated coefficients
compareOR4 <- data.frame(randomOpt4 = ORrandomOPT4[1:10], ORrandom4 = ORrandom4[1:10], random3 = ORrandom3[1:10], random2= ORrandom2[1:10], random0 = ORrandom, fixed = ORfixed)
kable(compareOR4, caption = ("nloptwrap model 4 compared"))
```

### Details

```{r}
summary(opt4)
```