---
title: "LogLink Logistic regression AQI data"
author: "Michael Andreae"
output: pdf_document
---

# Insurance status predicts antiemetic use 
we build a random effects model with procedure as random effects

```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr) # required to set options in Markdown R
library(lme4)
# library(nlme)
```



```{r, global_options, echo=FALSE}
# set options
opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
rm(list = ls())
everything<-FALSE
```

# Load cleaned complete case dataset
 
we load the cleaned dataset with procedure information *myAQI.Rdata* which we generated in the Project *AQI_Import*.   


```{r, load_clean_dataset, echo=TRUE}
load("Data/myAQI.Rdata")
str(myAQI)
```

# Four Predictors

## Fixed Effects Model 

Link : log 
fitted with glm with **four** predictors: 

formula0 <- ond ~ pay +age_group +sex

```{r, log0, echo=TRUE, eval=everything}

formula0 <- ond ~ pay +age_group +sex

fit_log0 <- glm(formula0, 
             family = binomial(link = "log"), 
             data = myAQI)
```

## Random Effects Model

fitted with glmer and procedure as random effect

```{r eval=everything, echo=TRUE}
formulaR0 <- ond ~ pay +age_group +sex + (1 | cpt)

m <- glmer(formulaR0, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"),
           nAGQ = 10)
save(fit_log0, m, file = "Results/zero.Rdata")
```


## Comparison of random versus Fixed effects model

```{r}
load("Results/zero.Rdata")
```

### Details Fixed Effects

```{r}
summary(fit_log0)
p_values <- summary.glm((fit_log0))$coefficient[,4]
ORfixed <- exp(coef(fit_log0)) # exponentiated coefficients 
# CI_fitlog<- confint(fit_log) # 95% CI for the coefficients, takes too long
kable(data.frame(ORfixed, p_values), digits = 3, caption = "Results log0")
```

### Details Random Effects

```{r}
summary(m)
ORrandom <- exp(m@beta) # exponentiated coefficients
```


### Random v. Fixed Side by Side 

```{r}
compareCoef <- data.frame(random=m@beta, fixed=coef(fit_log0))
kable(compareCoef, caption = ("Coefficients"))

compareOR <- data.frame(random=ORrandom, fixed= ORfixed)
kable(compareOR, caption = ("Odds ratios"))
```

# Five predictors

## Second Random Effects Model

fitted with glmer and procedure as random effect
adding ASA status

```{r eval=everything, echo=TRUE}
formulaR2 <- ond ~ pay +age_group +sex + ASA + (1 | cpt)

m2 <- glmer(formulaR2, data = myAQI, family = binomial, 
           control = glmerControl(optimizer = "bobyqa"),
           nAGQ = 10)

save(m2, file = "Results/second.Rdata")
```

```{r}
load("Results/second.Rdata")
```

### Details Second Random Effects Model

```{r}
summary(m2)
ORrandom2 <- exp(m2@beta) # exponentiated coefficients
compareOR2 <- data.frame(random2= ORrandom2[1:10], random0 = ORrandom, fixed = ORfixed)
kable(compareOR2, caption = ("Odds ratios random effects model 2"))
